Solent region: Test Maps

### 2021-07-30 Solent_Mapping_v2.Rmd
Added in looking at the cities in more detail for fuel poverty and also the 2018 fuel poverty map so straight comparisons can be made

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
head(lsoa_multidep)
lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf) +
  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
  scale_fill_continuous(name="IMD Score", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```

### Mapping Fuel Poverty
#### 2019 Fuel Poverty
```{r Loading in the LSOA 2021 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2019<-readr::read_csv (inFile)
head(lsoa_fuelpov_2019)
```

```{r Mapping the LSOA 2019 Fuel Poverty}
lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
####Mapping the difference in proportion of fuel poverty from 2012 to 2018

>>>>

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
head(lsoa_multidep)
lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf) +
  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
  scale_fill_continuous(name="IMD Score", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
#####Looking at the cities in more detail
```{r Looking at Southampton in more detail}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")

# plotting the multiple scales on dep of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `IMDScore`)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Looking at Portsmouth in more detail}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `IMDScore`)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Looking at Winchester in more detail}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Winchester")

# plotting the fuel poverty 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `IMDScore`)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Mapping Fuel Poverty
#### 2019 Fuel Poverty
```{r Loading in the LSOA 2021 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2019<-readr::read_csv (inFile)
head(lsoa_fuelpov_2019)
```

```{r Mapping the LSOA 2019 Fuel Poverty}
lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
#####Looking at the cities in more detail
```{r Looking at Southampton in more detail}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Southampton")

# plotting the fuel poverty 2019 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Looking at Portsmouth in more detail}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Looking at Winchester in more detail}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Winchester")

# plotting the fuel poverty 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```

#### 2018 Fuel Poverty
```{r Loading in the LSOA 2018 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2018 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2018<-readr::read_csv (inFile)
head(lsoa_fuelpov_2018)
```

```{r Mapping the LSOA 2018 Fuel Poverty}
lsoa_fuelpov_2018$LSOA11CD <- lsoa_fuelpov_2018$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2018_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2018) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2018_merged$pcFP18 <- as.numeric(lsoa_fuelpov_2018_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2018_merged) +
  geom_sf(aes(fill=pcFP18))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs) 2018")
```
#####Looking at the cities in more detail
```{r Looking at Southampton in more detail}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Southampton")

# plotting the fuel poverty 2019 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Southampton 2018")
```
```{r Looking at Portsmouth in more detail}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth 2018")
```
```{r Looking at Winchester in more detail}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")

# plotting the fuel poverty 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester 2018")
```
####Mapping the difference in proportion of fuel poverty from 2012 to 2018
